---
title: "map"
author: "Daniel Saggau"
date: "3/14/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##


```{r}
library(readxl)
library(sf)
library(ggplot2)

votes <- read.csv("~/Downloads/BelarusElections/belarus1994-qgisNew.csv",header=T)
geo = st_read("~/Downloads/BelarusElections 4/gis files for BLR and poland/BLR_Adm/BLR_adm2.shp", package="sf")
dist = st_read("~/Downloads/BelarusElections 4/gis files for BLR and poland/BLR_Adm/BLR_adm1.shp")
road = st_read("~/Downloads/BelarusElections 4/gis files for BLR and poland/BLR_rds/BLR_roads.shp")
road = readRDS("~/Downloads/gadm36_BLR_1_sf.rds")

```

```{r}
install.packages(c("cowplot", "googleway", "ggplot2", "ggrepel", 
"ggspatial", "libwgeom", "sf", "rnaturalearth", "rnaturalearthdata"))
```



```{r}
data <- read_excel("~/Downloads/df_merge_no.xlsx")
```
```{r}
library(stringr)
colnames(data)[3:14] = c("total", "received","took_part","part_early","part_residence","part_electionday", "dropped","against_all","invalid","commission","spoiled","unused")

data$region = str_to_title(data$region)
head(geo)
head(data)

merge = merge(road, data, by.x= 'NAME_1', by.y='region')
head(merg$lukashenko_share)
```

```{r}
#ggplot(data = merg) +
#    geom_sf() +
#    geom_sf(data = merg, fill = NA, color = gray(.5)) 
```

IAPT <- ggplot() +
  geom_sf(data = complete_CCG, mapping = aes(geometry = geometry, fill = complete_CCG$MeanWaitEnteredTreatment)) +
  scale_fill_viridis_c(trans = "sqrt", alpha = .4,
                       limits=c(0, max(complete_CCG$MeanWaitEnteredTreatment)),
#                       breaks = seq(from = 0, to = 2000, by = 500),
                       name ="Waiting time for before entering Treatment") +
  theme(panel.grid.major = element_line(color = gray(0.5),
                                        linetype = "dashed",
                                        size = 0.2), panel.background = element_rect(fill = "white")) +
  ggtitle("Waiting time for Mental Health Services in England",
          subtitle = "July 2017, IAPT") +
  labs(caption = "Source:https://digital.nhs.uk/data-and-information/publications/statistical/psychological-therapies-report-on-the-use-of-iapt-services",
       x = "longitude", y = "latitude")

```{r}

#sites <- st_as_sf(data, coords = c("longitude", "latitude"), 
#    crs = 4326, agr = "constant")
#plot = ggplot(data = merge) + 
#  geom_sf(data= merge, mapping = aes(geometry = geometry)) +
#  geom_sf(data = sites, size = 0.1, shape = 23, fill = "darkred")


map = ggplot()+ geom_sf(data = merge, mapping = aes(geometry = geometry, fill = lukashenko_share))

ggsave(filename = "map_votes.png",plot = map, width = 20,
       height = 10, device = "png", dpi = 150)

```

```{r}

lat <- 53.9
lon <- 27.566667
name <- "Minsk"

minsk_sf <- st_as_sf(minsk_df, coords = c("lon","lat"), crs = st_crs(4326))

library(skimr)
summary(merge$lukashenko_share)
skim(merge)

new = merge(dist, data, by.x = "NAME_1", by.y="region")
summary(new$geometry)
```

